On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-03-02 article/msculled.tex
omg is this my last chance to fire Kemp on this project??
spacing
diffuse not difuse

Here we use low resolution \lamost\ data to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium. The discovery (or non-discovery) of such stars guides models that attempt to explain the Mg--K anti-correlation and related abundance phenomena. In particular, such a search provides strong evidence either for or against the uniqueness of the progenitor stars to globular clusters. In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis for some of those candidates. In Section \ref{sec:discussion} we discuss our results and their implications for possible pollution mechanisms. Section \ref{sec:conclusion} summarises those results.

@@

\subsection{Association with known globular clusters}
\label{sec:globclustasoc}
We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}.

The spread in metallicity (Figure \ref{mhist}) is consistent with all candidates being field stars. The distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
No candidates have [Fe/H] $\approx -2$, the approximate metallicity of NGC 2419, nor are there many stars with [Fe/H] $\approx -1$, the metallicity of NGC 2808. Thus, we conclude that the candidates are not restricted to any specific metallicity, particularly not just to the metallicities of NGC 2419 and NGC 2808.

@@

Upon examining [Na/Fe] as estimated from the \lamost\ spectra, using the doublet around 5850 \AA, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances. However, the high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption. However, further investigation revealed no evidence of a difuse interstellar band (DIB) impacting spectra around the Na doublet, nor Mg or K. It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.

>>>>

Here we use low resolution \lamost\ data to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium. The discovery (or non-discovery) of such stars guides models that attempt to explain the Mg--K anti-correlation and related abundance phenomena. In particular, such a search provides strong evidence either for or against the uniqueness of the progenitor stars to globular clusters. In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis for some of those candidates. In Section \ref{sec:discussion} we discuss our results and their implications for possible pollution mechanisms.

@@

\subsection{Association with known globular clusters}
\label{sec:globclustasoc}
We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}. The spread in metallicity (Figure \ref{mhist}) is consistent with all candidates being field stars. The distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
No candidates have [Fe/H] $\approx -2$, the approximate metallicity of NGC 2419, nor are there many stars with [Fe/H] $\approx -1$, the metallicity of NGC 2808. Thus, we conclude that the candidates are not restricted to any specific metallicity, particularly not just to the metallicities of NGC 2419 and NGC 2808.

@@

Upon examining [Na/Fe] as estimated from the \lamost\ spectra, using the doublet around 5850 \AA, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances. However, the high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar
dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption. However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting spectra around the Na doublet, nor Mg or K. It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
